Asteroid project summary

### 2022-01-19 summaries/21-11/21-11.tex
Updated oblateness plot

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{oblateness.pdf}
  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet. Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
  \label{fig:oblateness}
\end{figure}

Figure \ref{fig:oblateness} shows no strong dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{20}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term. However, the fit parameter uncertainty does slightly decrease as oblateness increases on further study. \jtd{Give some quotes}. Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees. It is therefore reasonable to include that the presence of a large $J_{20}$ will not substantially affect the ability of this model to constrain asteroid interiors.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{oblateness.pdf}
  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet. Linear best fit lines (black, dotted) are plotted over the 1- and 2-$\sigma$ uncertainties. Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
  \label{fig:oblateness}
\end{figure}

Figure \ref{fig:oblateness} shows a slight dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{20}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term. However, the fit parameter uncertainty does slightly decrease as oblateness increases on further study. The trend of the decrease is linear, as shown by the close agreement between the overlaid best fit linear trend between the 1- and 2-$\sigma$ best fit uncertainties to the measured values. We compute an average slope by assuming that the true 2-$\sigma$ slope is twice the true 1-$\sigma$ slope, arriving at $\Delta \sigma / \Delta \epsilon = 1.9 \times 10^{-5}$ for $\gamma_0$, $1.35 \times 10^{-5}$ for $K_{22}$, and $1.8 \times 10^{-4}$ for $K_{22}$. Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees, however fitting these extra parameters is computationally more expensive. \jtd{I could scan over them}.
